The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, and Substructure Searching

### 2016-07-23 article.tex
Added some words on ring detection

  \subsubsection*{SMARTS parser}

  ....

@@

  .... \cite{May2014}

>>>>

  % \subsubsection*{SMARTS parser}

@@

  Ring finding is a key functionality in a cheminformatics library, and the CDK
  knows a long history of ring finding~\cite{May2014}. Particularly, non-redundant
  ring sets have seen particular interest, such as the smallest set of smallest
  rings, for which the CDK implements two classical algorithms~\cite{Figueras1996,Berger2004}.
  Recent work by one the authors has implemented a new, faster algorithm, allowing
  searching for various types of (non-redundant) ring sets~\cite{May2014}. These
  are available via the new Cycles API:

\begin{verbatim}
  allCycles = Cycles.all(mol)
  relevantCycles = Cycles.relevant(mol)
  essentialCycles = Cycles.essential(mol)
  sssrCycles = Cycles.sssr(mol)
\end{verbatim}
